---
title: "Ozone Variation over the City of New York"
author: "*Soumya Satyakanta Sethi*"
date: "18/08/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Details of airquality dataset

Daily readings of the following air quality values for May 1, 1973 (a Tuesday) to September 30, 1973.

- Ozone: Mean ozone in parts per billion from 1300 to 1500 hours at Roosevelt Island
- Wind: Average wind speed in miles per hour at 0700 and 1000 hours at LaGuardia Airport
- Temp: Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.
- Month:	numeric	Month (1--12)

## Variation of Ozone
```{r include=FALSE}
library(plotly)
aqr <- airquality
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
fig <- plot_ly(aqr, x = ~Wind, y = ~Ozone, mode = "markers",
        color = as.factor(aqr$Month), size = aqr$Temp)
fig
```
Size represents the variation in Temperature

## Reference
Chambers, J. M., Cleveland, W. S., Kleiner, B. and Tukey, P. A. (1983) Graphical Methods for Data Analysis. Belmont, CA: Wadsworth.


